\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-25 k-planar.tex
Boarding a flight now....

\begin{table}[h]
  \centering{
    \begin{tabular}{lccl}
      \textbf{Graph class} & \boldmath $\tw(H)$ & \boldmath $\ell$ & \textbf{Reference} \\ \hline
      planar & $3^*$ & $3$ & \cite{DJMMUW20} \\
      planar & $6^*$ & $1$ & \cite{UWY} \\
      genus $g$ & $3^*$ & $\max\{2g,3\}$ & \cite{DHHW} \\
%      genus $g$ & $2g+6$ & 1 & \cite{UWY} \\
      apex-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\
      % B-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\
      $k$-planar & $\binom{k+4}{3}-1$ & $18k^2 + 48k + 30$ & \cref{kPlanarProduct} \\
      $(g,k)$-planar & $\binom{k+4}{3}-1$ & $\max\{2g,3\}(6k^2+16k+10)$ & \cref{gkPlanarProduct} \\
      $(g,\delta)$-string & $\binom{\delta+4}{3}-1$ & $\max\{2g,3\}(\delta^4 + 4\delta^3 + 9\delta^2 + 10\delta+4)$ & \cref{StringProduct} \\
      $k$-nearest-neighbour & $O(k^6)$ & $O(k^4)$ & \cref{nn_product_structure} \\
      $d$-framed & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{d_framed_product_stucture} \\
      $1$-planar & $3^*$ & $7$ & \cref{1_planar_product} \\
      $d$-map & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{dMapProduct} \\
      $(g,d)$-map & $9$ & $\max\{2g,3\}\,(7d^2 -21d)$ & \cref{gdMapProduct} \\ \hline 
      \multicolumn{4}{l}{$^*$ these bounds also apply to the simple treewidth of $H$.}
    \end{tabular}
  }
  \caption{Known product structure theorems (of the form $G\subseteq H\boxtimes P\boxtimes K_\ell$).}
  \label{summary_table}
\end{table}

\note{DW}{why is the $2g+6$ commented out from the table?}

@@

\section{Framed Graphs, $1$-Planar Graphs, and (Plane) Map Graphs}
\label{FramedSection}

\note{DW}{Suggested section name ``Graphs Derived From Framed Graphs'' or just 
``Framed Graphs''}

@@

	The proof is by induction on the number of inner faces of $N_0$.  A particular easy case occurs when $N_0$ has no inner vertices, i.e., $V(N_0)=V(F)$. In this case we can simply take
	\note{DW}{Suggested revision, ``In the base case, $N_0$ has only one inner face, and we can simply take ...} 
  % \note{PM}{I debated what to put here since, even when $N'$ has only one face, the rules below work for picking $\tau$.  The \emph{real} base case occurs when $N'$ has zero faces, but that's not something that ever happens since we only ever apply induction on the inner faces of $M$ (except $\tau$).  I settled on this ``base case'' since it's clear that, in this case, the partition $\mathcal{P}$ is already decided.}
  \note{PM}{The longwinded version is that induction is on $(x,y)$ where $x$ is the number of inner vertices of $N_0$ and $y$ is the number of inner faces of $N_0$.  The base cases are $(0,y)$ for any $y$.  Unfortunately, we can't just induct on $x$ because it doesn't always decrease.} \note{DW}{We need to make it clear what we are doing induction on. 
I suggest we write, ``we proceed by  
induction on $(x,y)$ where $x$ is the number of inner vertices of $N_0$ and $y$ is the number of inner faces of $N_0$. ''}
	$\PP:=\{P_1,\ldots,P_k\}$ and verify that the preconditions of the lemma (the `setup') ensure that $\PP$ satisfies the requirements (i)--(iii):
	\begin{compactenum}[(i)]
		\item By definition, each of $P_1,\ldots,P_k$ is a part of $\mathcal{P}$.
		\item Assumption 4(b) ensures, for each $x\in V(H)$, the existence of $X_x$ and $Y_x$ such that $|X_x|\le d-3$ and $|Y_x\cap L_j|\le 3$ for each integer $j\ge 0$.
		\item The trivial tree decomposition of $H$ that has a single bag containing $\{x_1,\ldots,x_k\}$ is $3$-simple and, if $k=3$, has exactly one bag that contains $\{x_1,\ldots,x_3\}$.
	\end{compactenum}

>>>>

\begin{table}[h]
  \centering{
    \begin{tabular}{lccl}
      \textbf{Graph class} & \boldmath $\tw(H)$ & \boldmath $\ell$ & \textbf{Reference} \\ \hline
      planar & $3^*$ & $3$ & \cite{DJMMUW20} \\
      planar & $4^*$ & $2$ & \cite{bose.morin.ea:optimal} \\
      planar & $6^*$ & $1$ & \cite{UWY} \\
      genus $g$ & $3^*$ & $\max\{2g,3\}$ & \cite{DHHW} \\
      genus $g$ & $2g+6$ & 1 & \cite{UWY} \\
      apex-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\
      % B-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\
      $k$-planar & $\binom{k+4}{3}-1$ & $18k^2 + 48k + 30$ & \cref{kPlanarProduct} \\
      $(g,k)$-planar & $\binom{k+4}{3}-1$ & $\max\{2g,3\}(6k^2+16k+10)$ & \cref{gkPlanarProduct} \\
      $(g,\delta)$-string & $\binom{\delta+4}{3}-1$ & $\max\{2g,3\}(\delta^4 + 4\delta^3 + 9\delta^2 + 10\delta+4)$ & \cref{StringProduct} \\
      $k$-nearest-neighbour & $O(k^6)$ & $O(k^4)$ & \cref{nn_product_structure} \\
      $d$-framed & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{d_framed_product_stucture} \\
      $1$-planar & $3^*$ & $7$ & \cref{1_planar_product} \\
      $d$-map & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{dMapProduct} \\
      $(g,d)$-map & $9$ & $\max\{2g,3\}\,(7d^2 -21d)$ & \cref{gdMapProduct} \\ \hline
      \multicolumn{4}{l}{$^*$ these bounds also apply to the simple treewidth of $H$.}
    \end{tabular}
  }
  \caption{Known product structure theorems (of the form $G\subseteq H\boxtimes P\boxtimes K_\ell$).}
  \label{summary_table}
\end{table}

% \note{DW}{why is the $2g+6$ commented out from the table?}

@@

\section{Framed Graphs}
\label{FramedSection}

% \note{DW}{Suggested section name ``Graphs Derived From Framed Graphs'' or just``Framed Graphs''}

@@

  We proceed by induction on $(x,y)$ where $x$ is the number of inner vertices of $N_0$ and $y$ is the number of inner faces of $N_0$.  The induction base case occurs when $N_0$ has no inner vertices, i.e., $V(N_0)=V(F)$. In this case we can simply take
	% \note{DW}{Suggested revision, ``In the base case, $N_0$ has only one inner face, and we can simply take ...}
  % \note{PM}{I debated what to put here since, even when $N'$ has only one face, the rules below work for picking $\tau$.  The \emph{real} base case occurs when $N'$ has zero faces, but that's not something that ever happens since we only ever apply induction on the inner faces of $M$ (except $\tau$).  I settled on this ``base case'' since it's clear that, in this case, the partition $\mathcal{P}$ is already decided.}
  % \note{PM}{The longwinded version is that induction is on $(x,y)$ where $x$ is the number of inner vertices of $N_0$ and $y$ is the number of inner faces of $N_0$.  The base cases are $(0,y)$ for any $y$.  Unfortunately, we can't just induct on $x$ because it doesn't always decrease.} \note{DW}{We need to make it clear what we are doing induction on.
% I suggest we write, ``we proceed by induction on $(x,y)$ where $x$ is the number of inner vertices of $N_0$ and $y$ is the number of inner faces of $N_0$. ''}
	$\PP:=\{P_1,\ldots,P_k\}$ and verify that the preconditions of the lemma (the `setup') ensure that $\PP$ satisfies the requirements (i)--(iii):
	\begin{compactenum}[(i)]
		\item By definition, each of $P_1,\ldots,P_k$ is a part of $\mathcal{P}$.
		\item Assumption 4(b) ensures, for each $x\in V(H)$, the existence of $X_x$ and $Y_x$ such that $|X_x|\le d-3$ and $|Y_x\cap L_j|\le 3$ for each integer $j\ge 0$.
		\item The trivial tree decomposition of $H$ that has a single bag containing $\{x_1,\ldots,x_k\}$ is $3$-simple and, if $k=3$, has exactly one bag that contains $\{x_1,\ldots,x_3\}$.
	\end{compactenum}
